\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-11-01 redaction/JEGeo/revision_JEGeo/referees/answers/Answer_referee1.tex

        From this, we can deduce the confidence interval $CI^{ref}_{is} = \hat{\beta}_{is}^{max,ref} - \hat{\beta}_{is}^{min,ref}$.

        \item  Our method provides estimates of the underlying trade costs components ($\widehat{\tau}_i$, $\widehat{\tau}_s$, $\widehat{t}_i$, $\widehat{t}_s$) with an associated matrix of variance-covariance, from which we can rebuild $\beta_{is}$ (on a year-transport mode basis). As such, it does not yield an estimate of $\beta_{is}$ and an associated standard deviation, so that we cannot directly compare the precision of the estimation. We then deduce the accuracy of the $\beta$ estimate by relying on bootstrap method. Specifically, on a yearly/mode basis we draw a distribution of trade costs components and associated $\beta_{is}$ (10,000 random draws) from which we can compute the mean, the median and the 5-95 threshold values for each couple $i,s$. Noticing $\beta_{is}^{95}$ and $\beta_{is}^{05}$ the associated thresholds, we then obtain the confidence interval $CI_{is}= \beta_{is}^{95}- \beta_{is}^{05}$.\footnote{Notice that this should be made on the same sample as the one obtained with the referee's method, since the goal is to compare the accuracy of the $\beta_{is}$ estimate - implying to have the same sample of countries / sectors at first. }

    \item We can then evaluate the accuracy of each estimation method by comparing the size of the confidence intervals of the $\beta$, for each couple $i,s$ (by year and transport mode). We summarize this comparison in Figure \ref{fig:accuracy_beta}, which reports the distribution of the ratio of confidence intervals, taken in log.

    \begin{figure}[htbp]
    \caption{Accuracy of the estimation of the $\beta$: Comparison}
    \label{fig:accuracy_beta}
    \begin{center}
    \includegraphics[height=4in]{../../revised_article/comparaison_amplitude_baseline_referee1_2013_ves.png}
    \begin{minipage} [c]  {5in} \scriptsize%
    	    Note: Ratio of the confidence intervals = $ _{}ln(CI_{is}/CI^{ref}_{is})$
    \end{minipage}

@@

\subsection{Critique 2: Calculation of Unit Prices}

\textit{My second critique concerns the way the authors are calculating the unit prices.
The Census data reports the quantity of goods per observation. So, the authors
can calculate the unit price as Value/Quantity, which is consistent with how
price is modeled in standard trade models. Instead, the authors calculate unit
price as Value/Weight. This used to be a common exercise in the past where
many data-sets did not report Quantity. But, given their data, there is no
justification for the authors to calculate the prices this way.}

\textit{Calculating the unit price as Value/Weight presents the authors
with an additional endogeneity problem. To elaborate, let $\omega_{ik} = Weight/Quantity$
denote the unit weight of the goods in observation $ik$. [...] There is evidence that (i) $\omega_{ik}$ varies significantly within narrowly-defined product
categories, and (ii) $\omega_{ik}$ is negatively correlated with transport costs. So the
way the authors are calculating unit prices and estimating the model creates a
new (but avoidable) source of endogeneity.}

% MEMO: DO NOT FORGET TO REPORT THE ARGUMENTATION BELOW IN THE MAIN TEXT XXX
\paragraph{Our answer:}
\noindent This is a very important point we had not thought about, and we thank the referee for raising it.
The referee definitely has a point here, in the sense that Census data do report the quantity of goods (and sometimes even two quantities).
%At a more fundamental level, this raises the following question: Do we have reason to believe our measure of unit prices generate significant deviations from the one relying on quantities?
To that extent, the findings in \cite{Lashkaripour_JIE2020} were an eye-opener.
Based on US data very similar to ours over the period 1995-2015, the paper highlights, among other results, that the unit weight of imported goods is indeed substantially heterogeneous even within narrowly-defined product categories and the cost of transportation increases more rapidly with unit weight than the cost of production.  \cite{Lashkaripour_JIE2020} finds that accounting for the heterogeneity in export unit weights provides evidence in favor of the iceberg cost assumption regarding transport costs.
This result of transport costs close to be totally iceberg contrasts from our own findings of additive costs representing 30 to 45\% of total costs. Some elements can yet be put forward to account for the difference of results. Beyond a longer time span, our database is exhaustive, and encompasses all goods and industries, while \citet{Lashkaripour_JIE2020}) restricts to indivisible/discrete goods representing a bit more 56\% of US total imports of goods. In this regard, when comparing Tables 1 and 10 in \citet{Lashkaripour_JIE2020}, one can see that the share of multiplicative costs tends to decrease with the share of discrete goods. It is therefore reasonable to think that the inclusion of all goods, like in our setting, would move the average share of multiplicative costs far from 100\%.

Nevertheless, we did'nt want to stop at this very first argument. We indeed took the referee's remark very seriously and we did our best to address it to give you a convincing answer. It was not without difficulty yet, in particular due to data constraints. At a more fundamental level, we also believe that looking at transport costs on a per-weight basis do add relevant information. We develop each element of answer in what follows.

%We now report results based on per-unit prices.
%They confirm the results of \cite{Lashkaripour_JIE2020}
%Yet, first, looking at per-unit prices leads to leaving aside a large part of the data, both sectorally and chronologically.
%Second,  it is interesting to look at additive costs on a per-weight basis even there is a correlation between unit price and weight.

%The two stories are not necessarily incompatible, however.

@@

%Nevertheless, the point made by the referee is an important one and deserves careful investigation. We devoted a lot of thought to a potential switch from weight to quantity.
%Running the estimation considering quantities (i.e., units) rather than weight, still on the transport mode-yearly basis yet appears really uneasy in our context for several, non-trivial reasons, that we develop below.

\subsubsection{Data issues}

\paragraph{Availability issue} In our attempt to address the referee's remark, we faced a first difficulty regarding the availability of information on quantities. Neither the US Bureau of Census data nor the 1974-2004 Hummels' data (based on the Census Bureau data) do report the quantity by transport mode. This is incompatible with our empirical strategy of estimation transport costs which is conditional on the transport mode, similarly as in \cite{hummels2007}. As a result, to compute the unit price of all trade would require the assumption that the weight per unit is the same for vessel shipments and air shipments at the level of the observation. This is unlikely, as one would expect the higher-to-weight value to be transported by air rather than by vessel. The alternative would then be to only consider single-mode flows. In Hummels' data (1974-2014), on average 41.1 \% of trade flows and 79\% of trade value are multi-mode. Reducing the total value of the sample from 12,500 billion dollars to 2,650 billion dollars would entail of large loss of useful information. Original census data, when accessible (from 2002 because of the Covid situation), are more promising.\footnote{Original Census data are  reported at the HS-10 digit $\times$ district of entry $\times$ district of unleading $\times$ rate provision code.} In 2019, multi-modal flows are 570 billion dollars out of 1,790 billion dollars, or 31\% of the data. This is still a large share, but not too large to preclude any work. Accordingly, we dig deeper into this issue with the US Census dataset starting in 2002, restricted to single transport mode flows. \smallskip

The second difficulty dwells on the units used to measure quantities. The Census data, if it provides some information on quantity, remains silent on the units considered. To the best of our knowledge, these can only be found in the ``Harmonized Tariff Schedule of the United State''. Unfortunately, these schedules change many time per year and only the schedules from 2009 onwards were available in a .csv format. On the years for which the match could be done (from 2009), it turns out that at our sector level (3-digit), goods (either at the 5-digit or the 10-digit level) are measured in different units. In 2019, only 125 3-digit sectors out of 230 are measured in a single unit (after cleaning up the unit names\footnote{As units are not always coherent (eg weight can be given in ``kg’’, ``kg.'' ``Kg'' and, also, ``g'' and ``t'').}).\footnote{For instance, 3-digit SITC sector ``061 Sugar, molasses and honey'' includes among other products, 5-digit SITC product ``6150 Molasses, whether or not decolourized'', measured in liters and 5-digit SITC product ``06160 Natural Honey'' measured in kg. Actually worse than this, the 5-digit SITC product ``06190 Other sugars; sugar syrups; artificial honey (whether or not mixed with natural honey); caramel'' includes both 10-digit HTS product ``1702903500 Other: invert molasses'', measured in liters and 10-digit HTS product ``1702602200 Blended syrups described in additional u.s. note 4 to chapter 17: described in general note 15 of the tariff schedule and entered pursuant to its provisions''  measured in kilograms.} Neglecting these differences would invalidate our functional forms, as no one expects the transport cost of a ``piece'' to be the same as the transport cost of a ``kg'', even in the same sector.
So we are limited to using quantity units from 2009 to 2019, amending our structure of fixed effects to consider the triplet (origin country, sector, quantity unit).

\paragraph{Estimation issue} Getting deeper on the estimated functional form raised a third difficulty in adapting our equation to per-unit rather than per-weight prices. As discussed above, in our baseline regression we separate each transport cost component in its two distinct sector-origin country dimensions. As in \cite{Irrazabal_2015}, we assume an additive form for the additive cost, i.e. $t_{is(k)} = t_i+t_{s(k)}$ with $i$ the origin country and $s$ the sector. In the specific case of quantities, this raises a non-trivial issue for country-level fixed effects. Sector-level fixed effects could indeed be easily replaced by (sector,quantity unit) fixed effects; but the same does not appear relevant for country fixed effects. Let us develop on that.

In the per-weight price, the existence of a single country fixed effect applicable to all sectors could be justified, as a kilogram is always a kilogram and one can assume they both add the same to transport from, say, Germany. In contrast, an unit of tee-shirt is quite different from an unit of car. To clarify this point, assume imports of tee-shirts and cars from Germany and China. Under the separability assumption, importing a tee-shirt from either country implies paying the fixed effect for both countries (the same for all sectors) and the fixed effect for the sector (the same for all countries); and similarly for importing a car. Hence, the difference in the cost of importing a car from Germany versus China would be the same (in dollars) as the difference between the cost of importing a tee-shirt from Germany relative to China. This does not seem to us as a reasonable assumption; in this case specifically, we cannot keep the separability assumption.
As discussed before, this dramatically increases the computational difficulty of our method (with no substantial different results, see Subsection 3.3.1. in the main paper).\smallskip

Integrating these various constraints, we run this robustness check (weight versus quantity) \textit{i)} on a sample reduced over 2009-2019, considering single transport mode flows; all in all, this sample amounts to 66\% of the value of the baseline sample, \textit{ii)} retaining a non-separable structure of three-dimensional fixed effects $t_{is(k)u}$, $\tau_{is(k)u}$ where , according to the following equation:
\begin{equation}
\ln\left(\frac{p_{ik}}{p^u_{ik}}-1 \right)= \ln \left(\tau_{is(k)u} -1+\frac{t_{is(k)u} }{p^u_{ik}} \right) + \epsilon_{ik} \label{eq:model_IetA}
\end{equation}
\noindent where $p^u_{ik}$ refers to the unit price associated with quantity and $u$ to the unit considered to measure the quantity. Depending on the sector, two different units are considered, kilograms and numbers.

The results are reported in Table \ref{tab_comp_wgt_qty} and in Figure \ref{fig:beta_comp_wgt_qty}. In Table \ref{tab_comp_wgt_qty}, for each transport mode, the first column reports the estimation based on the price per quantity; while the second column reports the results obtained considering the price per kg on the same sample; the last column reported our baseline results on the large sample (considering the average value over 2005-2019, under the separability assumption).

@@

\begin{table}[htbp]
	\caption{Comparison: Price per quantity versus per kg, 2009-2019}
	\begin{center}		
		\input{../../revised_article/Online_Appendix/Comp_baseline_wgt_qy_reshaped.tex}
%		\input{../../revised_article/Online_Appendix/Comp_baseline_wgt_qy.tex}
{\parbox[l]{12cm}{ \vspace{4pt}\footnotesize{Notes: Time trend coefficient is the annual growth rate.}}}
\end{center}
	\label{tab_comp_wgt_qty}%
\end{table}%

\begin{figure}[htbp]
	\caption{$\beta$ Estimate: Price per quantity or price per kg, 2009-2019}
	\begin{center}
		\begin{tabular}{cc}
			\includegraphics[height=8cm]{../../revised_article/scatter_chronology_non_separe_wgt_non_separe_qy.png}\\
			\multicolumn{2}{l}{{\footnotesize Notes: In both cases, estimation is run without imposing the separability assumption.}}
		\end{tabular}
	\end{center}
		\label{graph_comp_wgt_qty}%
\end{figure}

These results show clearly that using price per unit (whatever that unit is) instead of price per weight decreases the share of additive costs (except if one look at the median for air). In this respect, they stand in line with the results of \citet{Lashkaripour_JIE2020}, stressing the correlation between weight per unit and unit price. Still, the share of additive cost is not reduced to zero, except if one looks at the median for vessel).
Thus these results do not disqualify our approach, especially as we cover a much larger period and sample with our baseline estimate.

\subsubsection{Why is price per weight interesting}
It is true that to study welfare, the relevant variable that would create distortions is the cost per unit. \textbf{Je trouve l'argument delicat car dans notre section modele, c'est justement le welfare qu'on regarde.} 
However, our primary aim is descriptive.

Our main objective in this paper is to provide a quantitative assessment of international transport costs over time; on that matter, one may start with the observation that transport cost schedules are expressed historically and currently in a mix per-weight and per-volume basis. \textbf{stop here}
For example, in 2021, air freight trade costs are expressed in weights, with a minimal weight per volume (``volumetric weight’’ or ``dimensional weight). See for example \href{https://transporteca.co.uk/shipping-costs}{https://transporteca.co.uk/shipping-costs}, \href{http://wap.dhl.com/serv/volweight.html}{http://wap.dhl.com/serv/volweight.html} and \href{https://en.wikipedia.org/wiki/Dimensional_weight}{ https://en.wikipedia.org/wiki/Dimensional\_weight}).
Maritime freight costs are expressed in volume.
Hence, looking at per-kg transport cost can be interpreted straightforwardly as trying to estimate the actual existing shipping costs, with sector fixed effects interpretable as measure of mean density for different sectors.
The existence of per-volume or per-weight shipping cost is a fact of (second) nature, directly linked to the technical constraints of the transportation sector.
The notion of per-unit shipping cost is one step removed from technical constraints and the functionning of the transportation sector.
The weight per unit is at least partly the result of a choice by firms.
To understand the context in which they operate, we find that studying the technical per-volume or per-weight shipping cost is interesting.

### 2021-11-01 redaction/JEGeo/revision_JEGeo/revised_article/Online_Appendix/online_appendix_DHP_rev1.tex
Graphique E5
Signed-off-by: Guillaume Daudin <gdaudin@mac.com>
Graphique D1
Signed-off-by: Guillaume Daudin <gdaudin@mac.com>

\begin{figure}[htbp]
\caption{Variance decomposition (observed cif-fas price gap)}
\label{fig:decomp_variance}
\begin{center}
\includegraphics[width=10cm, height=7cm]{variance_decomposition.pdf}
%{\footnotesize {OECD data} }
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
	\caption{$\beta$ Estimate: Price per quantity or price per kg, 2005-2019}
\label{fig:beta_comp_wgt_qty}
	\begin{center}
\begin{tabular}{cc}
	\includegraphics[height=8cm]{../scatter_chronology_non_separe_wgt_non_separe_qy.png}\\
\multicolumn{2}{l}{{\footnotesize Notes: In both cases, estimation is run without imposing the separability assumption.}}
\end{tabular}
	\end{center}
\end{figure}

\textbf{CHANGER LEGENDE PAS TRES BEAU - ENLEVER unweigthed}

@@

\begin{figure}[htbp]
\caption{Share of primary goods in the value of total US imports}
\label{fig:Share_prim_goods}
\begin{center}
\includegraphics[height=6cm]
{Share_of_primary.pdf}
\end{center}
\end{figure}

>>>>

\begin{figure}[htbp]
\caption{Variance decomposition (observed cif-fas price gap)}
\label{fig:decomp_variance}
\begin{center}
\includegraphics[width=10cm, height=7cm]{../Décomposition de la variance à la mimine_ss_val_ext.png}
%{\footnotesize {OECD data} }
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
	\caption{$\beta$ Estimate: Price per quantity or price per kg, 2009-2019}
\label{fig:beta_comp_wgt_qty}
	\begin{center}
\begin{tabular}{cc}
	\includegraphics[height=8cm]{../scatter_chronology_non_separe_wgt_non_separe_qy.png}\\
\multicolumn{2}{l}{{\footnotesize Notes: In both cases, estimation is run without imposing the separability assumption.}}
\end{tabular}
	\end{center}
\end{figure}

%\textbf{CHANGER LEGENDE PAS TRES BEAU - ENLEVER unweigthed}. Je crois que c’est bon.

@@

\begin{figure}[htbp]
\caption{Share of primary goods in the value of total US imports}
\label{fig:Share_prim_goods}
\begin{center}
\includegraphics[height=6cm]
{../Share_of_primary.jpg}
\end{center}
\end{figure}
